Notes for ISIPTA poster

### 2016-07-18 asce-paper.tex
Sec 4.3

We consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\footnote{Our approach would be possible also for other parametric lifetime distributions
that form a canonical exponential family
(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}).}
\begin{linenomath*}
\begin{align}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.%
\footnote{The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
or decreasing ($\beta_k < 1$) over time.
For $\beta_k=1$, we obtain the Exponential distribution with constant hazard rate as a special case.
The value for $\beta_k$ will thus often be clear from practical considerations.}
The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
we need to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

@@

Consider observing a prototype system until $\tnow$,
where the system has $K$ different types of components,
and for each type $k$ there are $n_k$ components in the system.
Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
there are $n_k - e_k$ components still functioning at $\tnow$.
We denote the corresponding vector of observations by
\begin{linenomath*}
\begin{align}
\mbf{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
\end{align}
\end{linenomath*}
where $t^+$ indicates a right-censored observation.
%
%***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
%introduce sets of observed and censored?

According to Bayes' rule, multiplying the prior density and the likelihood
(which accounts for right-censored observations through the cdf terms)
gives a term proportional to the density of the posterior distribution for $\lambda_k$:
\begin{linenomath*}
\begin{align}
%f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
% &\propto f_{\lambda_k}(\lambda_k)
%          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
%          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
f(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
 &\propto f(\lambda_k)
          \big[ 1- F(\tnow\mid\lambda_k) \big]^{n_k-e_k}
          \prod_{i=1}^{e_k} f(t_i^k \mid \lambda_k) 
\end{align}
\end{linenomath*}
Conjugacy is preserved and we get 
$\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
\begin{linenomath*}
\begin{align}
\nkn + 1 &= \nkz + e_k + 1 \\
\nkn\ykn &= \nkz\ykz + (n_k-e_k) (\tnow)^\beta + \sum_{i=1}^{e_k} (t_i^k)^\beta
\end{align}
\end{linenomath*}
are the updated parameters of the inverse gamma distribution.
%The posterior expectation for $\lambda_k$ is
%\begin{linenomath*}
%\begin{align}
%\E[\lambda_k\mid\nkn,\ykn] &= \ykn
%                            = \frac{\nkz}{\nkz + e_k} \ykz +
%                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} (\tnow)^\beta 
%                                                                    + \frac{1}{e_k} \sum_{i=1}^{e_k} (t_i^k)^\beta \Big]
%\end{align}
%\end{linenomath*}

@@

System survival calculated by %(see Risk Analysis paper eq. (7))
\begin{linenomath*}
\begin{align}
P(\Tsys > t) &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
\intertext{ and assuming components of different types are independent,}
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)
\end{align}
\end{linenomath*}
where the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$ for coherent systems,
and $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$.

A priori, we have, for $l_k = 0,1,\ldots, n_k$,
\begin{linenomath*}
\begin{align}
P(C^k_t = l_k\mid\nkz,\ykz)
 &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
\end{align}
\end{linenomath*}
under the assumption that components of the same type are independent given $\lambda_k$.

@@

For the situation with the system observed until $\tnow$, with data $\mbf{t}^k_{e_k;n_k}$,
we need the posterior predictive probability $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$.

For $l_k > n_k - e_k$, we must have $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) = 0$,
as at most $n_k - e_k$ components can function for $t > \tnow$.

%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\

A posteriori, we have, for $l_k = 0,1,\ldots, n_k - e_k$,
\begin{linenomath*}
\begin{align}
P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
 &= { n_k - e_k \choose l_k} \int [P_k(T \leq t \mid T > \tnow, \lambda_k)]^{n_k - e_k - l_k} \times \\ & \hspace*{2ex}
                              [1 - P_k(T \leq t \mid T > \tnow, \lambda_k)]^{l_k}
    f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k}) \dd \lambda_k
\end{align}
\end{linenomath*}

Now,
\begin{linenomath*}
\begin{align}
P_k(T \leq t \mid T > \tnow, \lambda_k)
 &= \frac{P_k(\tnow < T \leq t \mid\lambda_k)}{P_k(T > \tnow \mid \lambda_k)}
  = \frac{F_k(t\mid\lambda_k) - F_k(\tnow\mid\lambda_k)}{1-F_k(\tnow\mid\lambda_k)} \\
 &= \frac{e^{-\frac{(\tnow)^\kappa}{\lambda_k}} - e^{-\frac{t^\kappa}{\lambda_k}}}{e^{-\frac{(\tnow)^\kappa}{\lambda_k}}}
  = 1 - e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}
\end{align}
\end{linenomath*}

With this and the posterior substituted in, we get
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})} \\
 &= { n_k - e_k \choose l_k} \int \Big[1 - e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}\Big]^{n_k - e_k - l_k}
                                  \Big[    e^{-\frac{t^\kappa - (\tnow)^\kappa}{\lambda_k}}\Big]^{l_k} \times \\ & \hspace*{28ex}
    \frac{[\nkn\ykn]^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{[\nkn\ykn]^{\nkn + 1}}{\Gamma(\nkn+1)} 
    \times \\ & \hspace*{25ex}
    \int \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{(l_k + j) (t^\kappa - (\tnow)^\kappa) + \nkn\ykn}{\lambda_k}} \dd \lambda_k
\end{align}
\end{linenomath*}

The terms remaining under the integral form the core of an $\ig(\nkn + 1, \nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa))$,
allowing us to solve the integral using the corresponding normalization constant.
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})} \\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{13ex}  
    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
    \nkz + e_k + 1} 
\end{align}
\end{linenomath*}
for $l_k \in \{0,1,\ldots,n_k-e_k\}$.

We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.

Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
and summands whith even $j$ are decreasing in $t$,
while summands whith odd $j$ are increasing in $t$.
Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$
must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
and so the probability that $l_k$ of them remain operational must decrease.

@@

>>>>

We consider a system with components of $k=1,\ldots,K$ different types;
for each type $k$, there are $n_k$ exchangeable components in the system.
For each type $k$ component, we assume for its lifetime $T_i^k$ ($i=1,\ldots,n_k$, $k = 1, \ldots, K$)
a Weibull distribution with fixed shape parameter $\beta_k > 0$,
in short $T_i^k \mid \lambda_k \sim \wei(\beta_k,\lambda_k)$,
with density and cdf%
\footnote{Our approach would be possible also for other parametric lifetime distributions
that form a canonical exponential family
(see, e.g., \citeNP[p.~202 and 272f]{2000:bernardosmith}, or \citeNP[p.~8]{diss}).}
\begin{linenomath*}
\begin{align}
\label{eq:weibulldens}
f(t_i^k \mid \lambda_k) &= \frac{\beta_k}{\lambda_k} (t_i^k)^{\beta_k-1} e^{-\frac{(t_i^k)^{\beta_k-1}}{\lambda_k}}\,, \\
\label{eq:weibullcdf}
F(t_i^k \mid \lambda_k) &= 1 - e^{-\frac{(t_i^k)^{\beta_k}}{\lambda_k}} = P(T_i^k \leq t_i^k \mid \lambda_k)\,,
\end{align}
\end{linenomath*}
where $\lambda_k > 0$ and $t > 0$.%
\footnote{The shape parameter $\beta_k$ determines whether the hazard rate is increasing ($\beta_k > 1$)
or decreasing ($\beta_k < 1$) over time.
For $\beta_k=1$, we obtain the Exponential distribution with constant hazard rate as a special case.
The value for $\beta_k$ will thus often be clear from practical considerations.}
The scale parameter $\lambda_k$ can be interpreted through the relation
\begin{linenomath*}
\begin{align}
\E[T_i^k \mid \lambda_k] &= \lambda_k^{1/\beta_k}\, \Gamma(1 + 1/\beta_k)\,.
\label{eq:lambdainterpret}
\end{align}
\end{linenomath*}
For encoding expert knowledge about the reliability of the components,
we need to assign a prior distribution over the scale parameter $\lambda_k$.
A convenient choice is to use the inverse Gamma distribution,
commonly parametrized in terms of the hyperparameters $a_k > 0$ and $b_k > 0$:
%Conjugate prior is $\lambda_k \sim \ig(a_k,b_k)$:
\begin{linenomath*}
\begin{align}
f(\lambda_k\mid a_k,b_k) &= \frac{(b_k)^{a_k}}{\Gamma(a_k)} \lambda_k^{-a_k -1} e^{-\frac{b_k}{\lambda_k}}
\label{eq:ig-def}
\end{align}
\end{linenomath*}
in short, $\lambda_k \mid a_k, b_k \sim \ig(a_k,b_k)$.
The inverse Gamma is convenient because it is a conjugate prior,
i.e., the posterior obtained by Bayes' rule is again inverse Gamma and thus easily tractable;
the prior parameters only need to be updated to obtain the posterior parameters.

@@

Consider observing a prototype system until $\tnow$,
where the system has $K$ different types of components,
and for each type $k$ there are $n_k$ components in the system.
Denoting the number of type $k$ components that have failed by $\tnow$ by $e_k$,
there are $n_k - e_k$ components still functioning at $\tnow$.
We denote the corresponding vector of observations by
\begin{linenomath*}
\begin{align}
\vec{t}^k_{e_k;n_k} &= \big( \underbrace{t^k_1, \ldots, t^k_{e_k}}_{e_k \text{failure times}},
                             \underbrace{\tpnow, \ldots, \tpnow}_{n_k-e_k \text{censored obs.}} \big)\,,
\end{align}
\end{linenomath*}
where $t^+$ indicates a right-censored observation.
%
%***change to general right-censoring? So $n_k-e_k \to c_k$, $e_k+c_k=n_k$,
%introduce sets of observed and censored?

According to Bayes' rule, multiplying the prior density and the likelihood
(which accounts for right-censored observations through the cdf terms)
gives a term proportional to the density of the posterior distribution for $\lambda_k$:
\begin{linenomath*}
\begin{align}
%f_{\lambda_k\mid\ldots}(\lambda_k\mid\nkz,\ykz,\mbf{t}^k_{e_k;n_k})
% &\propto f_{\lambda_k}(\lambda_k)
%          \big[ 1- F_k(\tnow\mid\lambda_k) \big]^{n_k-e_k}
%          \prod_{i=1}^{e_k} f_k(t_i^k \mid \lambda_k) 
f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k})
 &\propto f(\lambda_k)
          \big[ 1- F(\tnow\mid\lambda_k) \big]^{n_k-e_k}
          \prod_{i=1}^{e_k} f(t_i^k \mid \lambda_k) 
\end{align}
\end{linenomath*}
Conjugacy is preserved and we get 
$\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k} \sim \ig(\nkn + 1, \nkn\ykn)$, where
\begin{linenomath*}
\begin{align}
\nkn + 1 &= \nkz + e_k + 1 \\
\nkn\ykn &= \nkz\ykz + (n_k-e_k) (\tnow)^\beta + \sum_{i=1}^{e_k} (t_i^k)^\beta
\end{align}
\end{linenomath*}
are the updated parameters of the inverse gamma distribution.
%The posterior expectation for $\lambda_k$ is
%\begin{linenomath*}
%\begin{align}
%\E[\lambda_k\mid\nkn,\ykn] &= \ykn
%                            = \frac{\nkz}{\nkz + e_k} \ykz +
%                              \frac{e_k}{\nkz + e_k} \cdot \Big[\frac{n_k-e_k}{e_k} (\tnow)^\beta 
%                                                                    + \frac{1}{e_k} \sum_{i=1}^{e_k} (t_i^k)^\beta \Big]
%\end{align}
%\end{linenomath*}

@@

The structure of complex systems can be visualized by reliability block diagrams,
an example is given in Figure~***.
Components are represented by boxes or nodes,
and the system works when a path from the left end to the right exists
which passes only through working components.
In a system with $n$ components, the state of the components can be expressed by the state vector
$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not.
The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
\cite{BP75}.
Most real-life systems are coherent,
which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
so system functioning cannot be improved by worse performance of one or more of its components.
Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.

The survival signature \cite{2012:survsign} is a summary of the structure function
for systems with $K$ groups of exchangeable components.
Denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,n_k$ for $k=1,\ldots,K$,
it is defined as the probability for the event that the system functions
given that precisely $l_k$ of its $n_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$.
Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$,
such that $\Rsys(t) = P(\Tsys > t)$ can be calculated using the law of total probability,
%System survival calculated by %(see Risk Analysis paper eq. (7))
\begin{linenomath*}
\begin{align}
P(\Tsys > t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                                                  P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
%\intertext{ and assuming components of different types are independent,}
             &= \sum_{l_1=0}^{n_1} \cdots \sum_{l_K=0}^{n_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k)\,,
\label{eq:sysrel-survsign}
\end{align}
\end{linenomath*}
where $P(C^k_t = l_k)$ is the (predictive) probability that exactly $l_k$ components of type $k$ function at time $t$,
and the last equality holds as we assume that components of different types are independent.
Note that for coherent systems,
the survival signature $\Phi(l_1,\ldots,l_K)$ is non-decreasing in each $l_k$.
%
%A priori, we have, for $l_k = 0,1,\ldots, n_k$,
%\begin{linenomath*}
%\begin{align}
%P(C^k_t = l_k\mid\nkz,\ykz)
% &= { n_k \choose l_k} \int [F_k(t \mid\lambda_k)]^{n_k-l_k}
%                        [1 - F_k(t \mid\lambda_k)]^{l_k} f_{\lambda_k}(\lambda_k\mid\nkz,\ykz) \dd \lambda_k
%\end{align}
%\end{linenomath*}
%under the assumption that components of the same type are independent given $\lambda_k$.

@@

In calculating the system reliability using \eqref{eq:sysrel-survsign},
the component-specific predictive probabilities $P(C^k_t = l_k)$
need to use all information available at time $\tnow$,
which, in the Bayesian framework,
are given by the posterior predictive distribution 
$P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$, $l_k = 0, 1, \ldots, n_k-e_k$. %$k=1,\ldots, K$.
(Remember that $e_k$ type $k$ components have failed by $\tnow$,
such that there are at most $n_k-e_k$ working components at time $\tnow$.)
%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
This posterior predictive distribution is obtained as
\begin{linenomath*}
\begin{align}
\lefteqn{%
P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\  %
 &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
                                  \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k
\label{eq:postpredtnow}
\end{align}
\end{linenomath*}
%
Now, by the Weibull assumption \eqref{eq:weibullcdf}, we have
\begin{linenomath*}
\begin{align}
P(T^k \leq t \mid T^k > \tnow, \lambda_k)
 &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
 &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
\end{align}
\end{linenomath*}
%
With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, we get
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \\
 &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}\times\\&\hspace*{27ex}
    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
    \times \\ & \hspace*{13ex}
    \int \lambda_k^{-(\nkn + 1) - 1} \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nkn\ykn}{\lambda_k}\Big\} \dd \lambda_k\,.
\end{align}
\end{linenomath*}
%
The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
with parameters $\nkn + 1$ and $\nkn\ykn + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
allowing us to solve the integral using the corresponding normalization constant.
We thus have, for $l_k \in \{0,1,\ldots,n_k-e_k\}$,
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{10ex}  
    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k)       (\tnow)^{\beta_k} }%
               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k-l_k-j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
    \nkz + e_k + 1} 
\end{align}
\end{linenomath*}

%Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
%once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
%and summands whith even $j$ are decreasing in $t$,
%while summands whith odd $j$ are increasing in $t$.
%Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$
%must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
%and so the probability that $l_k$ of them remain operational must decrease.

***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?

@@

***We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.
